---
title: "Willian's CV"
author: Willian Vieira
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume', 'https://cdn.rawgit.com/jpswalsh/academicons/master/css/academicons.min.css']
    self_contained: true
    includes: 
      after_body: ["assets/google-analytics.js", "assets/scale-to-fit.html"]
---

```{r, include=FALSE, cache = F}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(glue)
library(tidyverse)


# Holds all the links that were inserted for placement at the end
PDF_EXPORT <- FALSE

source('R/parsing_functions.R')

# Load csv with position info
position_data <- readr::read_csv('data/positions.csv')
```

Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa  fa-phone"></i> (263) 381-3636
- <i class="fa fa-envelope"></i> w.vieiraw@gmail.com
<!-- - <i class="fa fa-twitter"></i> [WillVieira90](https://twitter.com/willvieira90) -->
- <i class="fa fa-linkedin"></i> [Linkedin/WillVieira](https://linkedin.com/in/willvieira90)
- <i class="fa fa-github"></i> [GitHub/WillVieira](https://github.com/willvieira)
<!-- - <i class="fa fa-globe"></i> [willvieira.github.io/](https://willvieira.github.io/) -->
<!-- - <i class="ai ai-orcid"></i> [0000-0003-0283-4570](https://orcid.org/0000-0003-0283-4570) -->
- <i class="ai ai-google-scholar"></i> [Publications](https://scholar.google.com/citations?user=GyChlIoAAAAJ&hl=en)

<p style="margin-top: 0; margin-bottom: 1;font-size: 0.2rem;">
<br>
</p>

Skills
------------------------------------

<span style="font-weight:600;">Statistics, Modelling & Ecology</span>: <br>
Bayesian statistics · Nonlinear hierarchical models · SDMs · Sampling design · Spatial bias · Simulation · Sensitivity analysis · Uncertainty quantification · Model evaluation

<span style="font-weight:600;">Environmental & Geospatial Data</span>: <br>
Biodiversity monitoring · Forest inventory data · Climate and remote-sensing covariates · Habitat and vegetation data · Environmental assessment support · Decision-ready maps and reports

<span style="font-weight:600;">Programming & Scientific Software</span>: <br>
R · Python · Stan · SQL · Bash · DuckDB · Julia · Package development · Shiny · Quarto

<span style="font-weight:600;">Data Engineering & Reproducibility</span>: <br>
ETL pipelines · Metadata and data governance · Cloud object storage · Cloud-optimized geospatial access · Automated validation · Docker · CI/CD · Git · Unix · HPC · Make · Reproducibility

<p style="margin-top: 0; margin-bottom: 1;font-size: 0.2rem;">
<br>
</p>

Languages
------------------------------------

**Portuguese**<span style="font-size:11px;"> · Native</span><br>
**French**<span style="font-size:11px;"> · Full Professional</span><br>
**English**<span style="font-size:11px;"> · Full Professional</span><br>


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r footer, results='asis'}
# Resolve the application tag with precedence: env var > data/application_tag.txt > none
app_tag <- trimws(Sys.getenv('CV_APP_TAG', unset = ''))
if (!nzchar(app_tag)) {
  tag_file <- 'data/application_tag.txt'
  if (file.exists(tag_file)) {
    lines <- readLines(tag_file, warn = FALSE)
    lines <- trimws(lines)
    lines <- lines[nzchar(lines) & !startsWith(lines, '#')]
    if (length(lines)) app_tag <- lines[1]
  }
}

base_pages <- 'https://willvieira.github.io/cv'
base_repo  <- 'https://github.com/willvieira/cv'
if (nzchar(app_tag)) {
  html_url   <- paste0(base_pages, '/', app_tag, '/index.html')
  pdf_url    <- paste0(base_pages, '/', app_tag, '/WillianVieira.pdf')
  source_url <- paste0(base_repo,  '/tree/', app_tag)
} else {
  html_url   <- paste0(base_pages, '/index.html')
  pdf_url    <- paste0(base_pages, '/WillianVieira.pdf')
  source_url <- base_repo
}

cat(sprintf(
  paste0(
    '<div class="cv-footer">',
    '<a href="%s"><i class="fa fa-github"></i> Source</a> · ',
    '<a href="%s"><i class="fa fa-globe"></i> HTML</a> · ',
    '<a href="%s"><i class="fas fa-download"></i> PDF</a>  ',
    'Updated %s',
    '</div>'
  ),
  source_url, html_url, pdf_url, format(Sys.Date())
))
```


Main
================================================================================

<span style="font-weight:600">Willian Vieira</span> <span style="font-size: 15px;">PhD</span>{#title}
--------------------------------------------------------------------------------

<p style="text-align:justify;margin-top: 4px; margin-bottom: 0;">
  PhD quantitative ecologist with data engineer experience. I build statistical models, reproducible workflows, and environmental data infrastructure that turn complex biodiversity and geospatial data into analyses people can inspect, trust, and reuse.
</p>

Data Science & Engineer Experience {data-icon=briefcase}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'experience')
```

Education {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```

<!-- 
Research Experience {data-icon=laptop}
-------------------------------------------------------------------------------- -->

```{r,eval=FALSE}
print_section(position_data, 'research_positions')
```


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r,eval=TRUE}
print_section(position_data, 'teaching_positions')
```

Training {data-icon=certificate}
--------------------------------------------------------------------------------

```{r,eval=TRUE}
print_section(position_data, 'training')
```


Publications {data-icon=book}
--------------------------------------------------------------------------------

### Unifying individual and metapopulation scales with stochastic population models: the effect of climate and competition on tree range limits

In production. Preprint hosted on <a href="https://willvieira.github.io/ms_forest-suitable-probability/" target="_blank"><i class="fa fa-github"></i></a>

N/A

2026

<span style="text-decoration: underline;">Vieira, W.</span>, Gravel, D.       

### Sensitivity of tree species demography to climate and competition across their range

Under review. Preprint hosted on <a href="https://willvieira.github.io/ms_forest-ipm-sensitivity/" target="_blank"><i class="fa fa-github"></i></a>

N/A

2026

<span style="text-decoration: underline;">Vieira, W.</span>, MacDonald, A., Gravel, D.       

```{r,eval=TRUE, warning = FALSE,message = FALSE}
myORCID <- '0000-0003-0283-4570'
underlineName <- 'Vieira, W.'

# get edited publications from ORCID id
pubs <- get_publications(myORCID, underlineName)

print_publications(pubs)
```

<!-- 
Selected Talks and Posters {data-icon=chalkboard-teacher}
-------------------------------------------------------------------------------- -->

```{r,eval=FALSE}
print_section(position_data, 'talk_poster')
```
