---
title: "Willian's CV"
author: Willian Vieira
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume', 'https://cdn.rawgit.com/jpswalsh/academicons/master/css/academicons.min.css']
    self_contained: true
    includes: 
      after_body: ["assets/google-analytics.js"]
---

```{r, include=FALSE, cache = F}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(glue)
library(tidyverse)


# Holds all the links that were inserted for placement at the end
PDF_EXPORT <- FALSE

source('R/parsing_functions.R')

# Load csv with position info
position_data <- readr::read_csv('data/positions.csv')
```

Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> w.vieiraw@gmail.com
<!-- - <i class="fa fa-twitter"></i> [WillVieira90](https://twitter.com/willvieira90) -->
- <i class="fa fa-linkedin"></i> [Linkedin/WillVieira](www.linkedin.com/in/willvieira90)
- <i class="fa fa-github"></i> [GitHub/WillVieira](https://github.com/willvieira)
<!-- - <i class="fa fa-globe"></i> [willvieira.github.io/](https://willvieira.github.io/) -->
<!-- - <i class="ai ai-orcid"></i> [0000-0003-0283-4570](https://orcid.org/0000-0003-0283-4570) -->
- <i class="ai ai-google-scholar"></i> [Publications](https://scholar.google.com/citations?user=GyChlIoAAAAJ&hl=en)


Quantitative
------------------------------------

Bayesian statistics, Hierarchical models, Random Forest, Mathematical modelling, Regression

Dev stack
------------------------------------

<span style="font-weight:600;">Data analysis</span>: <br>R, Python, Julia, Stan, HPC<br>

<span style="font-weight:600;">Data base</span>: SQLite<br>

<span style="font-weight:600;">Automation/reports</span>: <br>markdown, pandoc, Quarto,<br>LateX, bash, makefile<br> 

<span style="font-weight:600;">Web</span>: HTML/CSS, ShinyApp<br>

<span style="font-weight:600;">DevOps (CI/CD)</span>: Git, GitHub, Docker, GitHub Actions


Languages
------------------------------------

**Portuguese**<span style="font-size:11px;"> Native</span><br>
**French**<span style="font-size:11px;"> Full Professional</span><br>
**English**<span style="font-size:11px;"> Full Professional</span><br>


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

The source code is available at [github.com/willvieira/cv](https://github.com/willvieira/cv).

Last updated on `r Sys.Date()`.

[<i class='fas fa-download'></i> Download the PDF version](https://willvieira.github.io/cv/WillianVieira.pdf)


Main
================================================================================

<span style="font-weight:600">Willian Vieira</span> <span style="font-size: 15px;">PhD</span>{#title}
--------------------------------------------------------------------------------

<p style="text-align:justify;margin-top: 6px; margin-bottom: 0;">
  Trained as a quantitative ecologist, I learned to make sense of messy, complex natural systems. There, I immersed myself in statistics to tell compelling stories with incomplete data, accounting for uncertainty and bias every step of the way.
</p>
<p style="text-align:justify;margin-top: 5px;margin-bottom: 0;">
  Now I channel that same scientific rigor into full-stack data engineering, building reproducible and automated data pipelines designed to scale. My mission is to make data accessible and actionable for everyone, from scientists to executives.
</p>

Experience {data-icon=briefcase}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'experience')
```

Education {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'research_positions')
```


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'teaching_positions')
```

Training {data-icon=certificate}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'training')
```


Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r, warning = FALSE,message = FALSE}
myORCID <- '0000-0003-0283-4570'
underlineName <- 'Vieira, W.'

# get edited publications from ORCID id
pubs <- get_publications(myORCID, underlineName)

print_publications(pubs)
```


Selected Talks and Posters {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'talk_poster')
```
